---
title: "Alcohol vs Seat choice"
author: "Julianne Mercado"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually the plot shows a large difference between the back row and the middle row. Though it makes a large difference, it makes an even bigger difference between the back row and front row.  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

Based on the chart, the back row drinks 8.5 more drinks than the middle row, drinking 3.3 drinks per week. The front row drinks 1.7 per week. It is reasonable to assume that they are noot drinking the same amount. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of getting the result like we just obtained if the null hypothesis is actually true. Since the result is so small I reject the null hypothesis. 

## Conclusions


